\documentclass[final,5p,times,twocolumn,authoryear]{article}
\usepackage{cite}
\begin{document}

\title{Literature Review}
\author{Jiazhi Zhou}
\maketitle

\begin{abstract}

This literature review contributes to the research towards better
embodiment experience in VR technology. The results of this review will
allow the research team to deploy the appropriate model for the given
purpose of the experiments and observe the reactions of users to the
model.

\end{abstract}

\section{Introduction}

TODO: write

\section{Existing work}

TODO: write

% introduction

% topic overviews

\subsection{Human-Co-Creative-Agent Interaction}
% introduction leading to topics
Interaction design in Human-Robot co-creative systems are important.
Studies have shown that a system with good interaction design, like
providing feedback, allowing for multiple people to interact, etc. have
proven to improve people's perception and attitude towards to the AI,
and be more inspired, and lead to facilitating positive social
interactions \cite{Long2019, Rezwana2022}. Kantosalo et al. said that:
interaction design should be ground zero for designing co-creative
systems \cite{Kantosalo2020}.  Despite this, many AI research failed to
consider this, and focus on the model but neglect the interaction
\cite{Rezwana2023}. So to ensure our agent will have high quality
interactions with the users, we gather important interaction design
requirements from all the critical stakeholders, including professional
dancers, and the general public alike. This will first be done, through an literature
review and analysis of critical modern co-creative AI systems. And a
dive into the interaction design and analysis space will be done, in
order to facilitate a more systemic way to design and study these
interactions.

\subsubsection{Requirements and Expectations on Co-Creative Interaction Systems}
% review of wallace's workshop
Wallace et al. performed a workshop studying the expectations from
professional dancers for an AI dance partner \cite{Wallace2023}. The workshop introduced to
the dancers on a high level, how a dance generation AI would work. The
dancers are then put into pairs, where one of the dancer from the pair
would explore the role of an AI dancer, and the other one would explore
the role of the user of the AI. The workshop ended with a qualitative
feedback session which resulted in important insights into co-creative
process for dancers. One important theme that a lot of the dancers
mentioned in their feedback was "shared images", more specifically,
having a shared language and understanding of their work, and then,
breaking of the image, allowing them to continue the creative process
exploring other directions, when the current creative direction runs
dry. Another theme was that human dancers would eventually get tired, or
experience physical constraints to their body, but they thought AI
dancers can explore impossible positions which can act as inspiration
rather than a negative. The final theme was that dancers have the
intuition to perdict what their partner will do, resulting in a more
fluid interaction process and allowing them to not look at each other
all the time. This also comes from having a shared image or
understanding of the creative process. These themes should be taken into
consideration for how a dance generation AI should behave from the
perspective of professional dancers, however, this could differ for
non-dancers.

% review of d longs article on public installation design
LuminAI is a good example of existing modern co-creative dance agent. In
a 2019 article, the creators of LuminAI, aka Long et al., analyzed many
existing co-creative agents in public installations (including LuminAI),
and identified interaction design principles that creates a better
interaction experience. There are many design principles that this
article identified, including technology design and research design, we
are mostly interested in the design principles related to interaction
design. The first interaction design principle is to have multiple entry
points for interaction. What this means for our research, is to consider
interaction of both non-dancers as well as dancers to have a good
experience, which should allow for a more inclusive experience. The
second point, is to allow for group interaction, and also try to,
through the installation, facilitate human collaborations.  This could
mean, for the non-dancers, bring people to dance together on the floor,
and for dancers, allow multiple dancers to dance together.  The ability
for the model to allow for both experienced dancers and non-dancers
raise a interesting challenge. As we have identified many differences in
the preferred interaction styles of the general public compared to
professional dancers. But designing with the use of both groups in mind
can help bridge the gap and allow for a general design.  Allow for
multiple dancers to interact becomes a challenge to the AI model, but
there can be ways to average the data before or after the information
gets passed to the model for inference, that can be used to avoid
increased training complexity.

% review of LuminAI related research, adding leadership state awareness
Winston and Magerko explored the interactions of non-dancers with the
aforementioned interactive public installation: LuminAI, and designed a
new interaction framework for LuminAI and named it TT-VAI
\cite{Winston2017}. TT-VAI differed from the base version, as it not only
follows the user but sometimes would try to lead the dance.  The AI
would uses metrics such as energy, temp, and size, as turn-taking cues,
to know when to
take the lead, and when to give it back to the user. Through
observations, Winston and Magerko identified common turn-taking cues
that dancers use, when performing lead-partner dances.  This included
gaze, haptic feedback (in the form of applying pressure to the
follower's arm), and energy. Gaze and haptic are left out of the
decision making model of TT-VAI as those two are not good communication
channels for a projected agent. The base version of LuminAI and TT-VAI
are studied in a user study. Out of the two versions of the model, the
turn taking model was disliked by a few users, who preferred less
"back-and-forth" and preferred more natural interactions and felt more
inspired. Two users preferred the turn-taking model as it was providing
more than just mimicking. However, mimicry showed positive feedback from
several participants of the user study, since the agent is deemed "more
responsive to my movement." The research highlighted interesting ideas
in how a sense of leadership state effect's the user's perception of the
model, and how mimicry or being a follower by the model can provide
benefits for improved user perception. It also highlighted issues with
this interaction framework, like the existence of intersubjectivity for
who the leader is.

% review of RTC, improvisation for professional and non-dancers
Turn-taking in improvisational settings are studied by Evola et al.
\cite{Evola}, where clear distinctions between how turn-taking happens
for seasoned dancers, and non-dancers are observed.  An improvisational
performance is used as the context for the user study, where users in a
group of 6 can take turns to construct an art piece from an assortment
of items placed on a table in the centre of the stage. The turn-taking
sections of the performances are picked out and analyzed.  One major
different identified, between expert performers and the non-dancers,
were the expert performers did not performing any "communicative
movement", but rather using observations from their parafoveal and
peripheral vision to take cues, while the non-performers were seen
exchanging gazes to communicate. This revealed that expert dancers can
be way more intuitive during an improvisation which leads to a fluid and
seemless performance, while non-dancers often hesitate, and want more
explicit communication and turn-taking cues. In trying to explain the
non-dancer's hesitence, another idea generated, was the non-dancers
wanted approval and to please the choreographer, which is why there was
an increased amount of hesitation. This is possibly resulted from the
context of the experiment, where the turn-taking is in a "performance"
which has a certain level of strictness engrained in people's minds,
leading to nerve.

% quick analysis of intuition flow
The idea of intuition flow aligns well with what Evola et al. discovered
from their experiment with the professional dancers \cite{Wallace2023,
Evola}. The idea of intuition was the result of a discussion involving
how professional dancers were able to remove intersubjectivity during
the turn-taking excersize without using communicative movements. Evola
et al. discussed how the dancers perhaps viewed the excersice not as
turn-based creation of art, but just the creative process in itself, so
there was no thoughts of when should I take a turn, but rather, everyone
were on the same page, and were connected, allowing them to form a
"coordinated communication behaviour". The way Wallace et al. discussed
this behaviour was that: dancers do not think, but simply do. The
intuition is what tells the dancers what to do during an improvisation.
This could mean that we can try to train AI to pick up on the
"coordinated communication behaviour" and act like they understand as
well, or use a different interaction framework, and simply have the AI
try to contribute to the "art piece" (the dance), and use a feedback
system to know how well it is interacting, and contributing.

% analysis of intuition flow with non-dancers, and what they means for
% the interaction framework.
It is, however, crucial to think about how the intuition flow comes into
play with non-dancers. From Evola et al.'s study, we realized that
non-dancers were not using a "coordinated communication behaviour". This
problem also surfaced from Zamm et al.'s study \cite{Zamm2023}, where
users attempt to learn to tap to a rhythm in a pair. The study first had
users learn to tap by themselves, then they were put into pairs. The
result showed that the users were unable to produce the same result as
they did by themselves, in a pair, even when they have had some practice
by themselves already. This shows that the ability for non-dancers to
grow the intuition to move with any dance partner without thinking, over
the course of playing with the installation, or in any short user study
settings, is likely impossible. However, the need for a smooth
interaction was highlighted from Winston and Magerko's work, where users
that preferred the base version of LuminAI thought it had less "back and
forth", and preferred a more natural interaction. This means, people do
not dislike turn-taking, but simply dislike the unnaturalness to it.
This view aligns with the study of conversational turn-taking
\cite{Thomaz2011}, where traditional conversational turn-taking
interaction between human and robots feel awkward because of either
pausing too long, or talking over the human because of awkward and
non-agreed turn-taking cues. But since non-dancers are unable to
turn-take well with others either, since they are unexperienced, perhaps
it is good to have turn-taking be an optional feature and simply have
the AI try to produce as natural interaction as possible.

% analysis of mimicry
While the experts want an improvisational dance to be about the creative
process, general public could want different things. From Winston and
Magerko's work, we learn that mimicry was preferred by some of the
participants, as they liked it when the agent was responsive to their
movements. This is true in some levels for professional dancers, as
Wallace et al. observed that the dancer pairs would often indirectly
mimic their partner. This means mimicing of the movement trajectory etc.
but never mimicking the movement exactly. As Evola et al. and Wallace et
al.discused, the process of creation is not viewed by the dancers as
granular interactions but the dance as an art piece as a whole. So
interaction framework for interacting with a professional dancer should
be about the creative process and the "product" (in a non-physical
sense), while interaction with the general public could be more on a
granular level, where certain movements or ways of interactions could be more
inspiring to facilitate group interaction and get more people to be involved.
 
% analysis of glitches
Wallace et al. discussed, how the existence of glitches could positively
effect the professional dancers, since it gave them new ideas. However,
the glitching when shown to the general public, could be an issue as
glitchy movements could potentially deter users and make them think the
AI is faulty and bad. As the main goal of professionals using the AI
would be to get inspired and keep the improvisation going, while the
main goal for a public installation would be to get people involved and
be inclusive, these differences could mean that only one model can be
explored in this research project due to time and resource cost.
However, the design principle from \cite{Long2019} also mentioned that
public installation AI systems should be designed with modularity and
maintainablity in mind, so if we use the principles of modularity, we
can potentially design general modules that both of these interaction
frameworks will be able to adopt, and then have specialized modules that
differ between the professional model and the public installation model.
This would also allow the agent to be shown to a wider range of people,
allowing for more feedback and expose more people to co-creative AIs.

\subsection{Interaction Framework}
% review of COFI
Rezwana and Maher proposed a novel framework for designing co-creative
interaction called the COFI which can help put the requirements gathered
from the above section into more concrete terms, as well as confirming
some ideas that we had. This framework breaks the co-creative
interaction down to low level aspects. This includes: what collaboration style
and communication style does the framework have, is the creative process
a generative process, or a evaluation process or a definition process, how does the AI
contribute to that process, and how much should the AI contribute
compared to the human contribution. The exact framework breaks this down
in a bit more detail, but as an overview, COFI allows us a way to group
different interaction frameworks and compare them to each other. After
proposing the COFI framework, Rezwana and Maher identified and evaluated
a list of co-creative systems and sorted them using COFI. The results
highlighted 3 Human-AI co-creative interaction frameworks. The first
being an agent to follows and complys with human contributions, and
generate similar contributions. This is a pleasing agent, which can be
good for extending human's creativity. The opposite of a pleasing agent
is a provoking agent, but both pleasing and provoking agents play
important roles in co-creative systems. The second is models that uses
spontaneous initiative-taking and creates in parallel with users. This
would align more with the improvisational dance agent. However, the main
issues with this domain of models is the lack of communication flow from
the agent to the user, which can negatively impact the quality of
collaboration and user experience. The thrid cluster of models is an
advisory and evaluation type of agent, where the agent would provide
feedback and can refine the user's deisgn. However, this model lacks the
communication channel from user to the agent. Overall, the three main
clusters all have their pros and cons, and ensuring good communication
between the agent and the user would be crucial for a good user
experience and collaboration quality.

\subsubsection{Analysis}
% analysis of COFI
% analysis of differences between professional and non-dancers using
% COFI
In the first cluster of models, where the agent would follow and comply
with the human contributions could be looked into for a co-creative agent.
The difference between how professional wants to interact with the AI
agent and how the public would likely want to interact with the AI agent
fits nicely into the COFI framework. The COFI framework analysis brought
up the ideas of "pleasing agent" and
"provoking agent". Where pleasing agent can perform the action of
extending one's creativity, like Text-To-Image generation AIs bringing user's idea to life. The
place for pleasing agent for professionals in general, however, is
uncertain, and a specific user study for this can be conducted for
professional dancers in order to learn whether the "pleasing" quality of
a co-creative agent could also benefit professional dancers in achieving
their creative ideas. Pleasing agents are also identified as being able
to follow the user's style and artistic vision. That aspect might
fit better into the use of a co-creative agent for improvisational dancers.
Provoking agents, like using glitches to inspire
dance \cite{Wallace2023}, and "breaking of shared images" seem to fit better for professionals where
their goal is to generate new ideas. However, with the non-dancers from
Winston and Magerko's work, out of the 6 people who understood which
version mimicked more, 2 of them liked TT-VAI (turn-taking version
of LuminAI) better, quote: "seemed like it was doing more” and “seemed
more ready to throw something into the party." This demonstrates that
a provoking agent might not strictly be applicable for professionals
while a pleasing agents also might not be strictly for the general
public.

% analysis of cluster two
The second cluster of co-creative agent interaction framework has a more
aligned theme with our study of improvisational dance agent. The idea of
mimic and non-mimic agent is a critical part of this cluster of agents.
As discussed previously, mimicry can have its place in both non-dancer
and dancer interactions, but no strict mimicry of moves should be used
when interacting with a professional dancer. However, a big pitfall with
these models, is a lack of Agent-To-Human communication which negatively impacts
the interaction. The importance of a two-way communication is studied
more concretely by Rezwana and Maher in an earlier article
\cite{Rezwana2022}, where a user study demonstrated that adding a
communication channel from agent to the user can significantly improve
user experience and perception to the agent, and improve the users'
ability to create. However, communication in an embodied way is a
challenging task in itself, since we saw that professional dancers often
does not "communicate" but rather use their instincts to work together.
This makes creating a meaningful Agent-To-Human feedback channel rather
challenging. But using other means of communications that the user could
understand better, like visuals, audio, and even text could be attempted
in order to study its proficiency and effect on the interaction.  This
communication channel could also be implemented as a module for ease of
swapping in and out, for different use cases of the model.

% analysis of cluster three
The third cluster, of an advisory and evaluation agent could be counter
intuitive for an embodied interaction. However, the fact the cluster
three and cluster two complements each other prompts the ideas of
combining two agents into one, where one would simply dance, and another
would evaluate the creative process and creative product which would act
as a way to give feedback to users during the process. The mode of
communication for Agent-To-Human, would still be important to figure
out. This also prompts the thinking of where does this agent live, as a
visualisation could live right in the 3D space, but a UI could
potentially break immersion or even distrupt an professional dancers
intuition. The study of effective ways to deliver.

% TODO: refactor using the 3 frameworks identified to be suitable for
% human ai co-creative interaction

% overview of COFI and co-creative interactions
% The requirements generated from Wallace's work, can be put into the COFI
% framework to solidify interaction desgin when the AI interacts with an
% expert dancer. Intuition flow identifies that there would be no distinct
% communication between the human and the AI, and the communication style
% should all be embodied, and the timing of initiatives should also be
% spontaneous. The dancers from Wallace's workshop identified that the
% person pretending to be the AI, showed little mimicry, and more
% similarity of movement direction and trajectory. This means expert
% dancers would likely expect a non-mimicry style. The rest of the
% framework is filled in from how a improvisational dance would happen.
% Certain points are not very obvious and require further understanding
% and analysis. Task distribution could be viewed as both the human and
% the AI are dancing. But this can also be viewed as one person is
% performing the task of leading, and the other is performing the task of
% following, and since in the article, Rezwana and Maher mentioned how
% performing the same task often requires turn-taking, this shows us that
% we should model the task as being, leader and a follower, and the tasks
% are performed in parallel. For the contribution type, it is challenging
% to pin point to one, since the dancers from Wallace's work mentioned
% that, their partner should both build onto their movements, so extend
% and transform, or that their partner should break the shared image, so
% create new. But the embodied co-creative system should perhaps be
% viewed, not as the movement in the moment, but as the entirety of the
% dance.

\subsection{Interaction Labeling and Analysis}
% introduction leading to methods
Interaction, especially embodied interactions like dance, is a
challenging thing to analyse. But having proficient tools to analyze the
data after gathering information will be critical in generating further
insights, and comparing different models against each other on
meaningful metrics. This prompts a look into recent, and novel methods
for measuring, analyzing and labeling co-creative, and embodied interactions.

% CSI

% OCSM

% EVERYTHING BELOW ARE UNORGANIZED
% One interesting difference spoted between Winston and Magerko's work, and
% Wallace et al. and Evola et al.'s is that Winston and Magerko identified explicit
% turn-taking cues while both Wallace and Evola identified the lack of
% obvious cues displayed when dancing. This difference can be from the
% forms of dancing that they studied, since Winston and Magerko studied
% """ and Wallace et al. and Evola et al. both studied improvisational
% dance. This could mean that either turn-taking is a way more natural
% process in improvisational dance, and there are no clear leader or
% follower, or that the dancers do not have a clear idea of who is leading
% and who is following, but simply "do", quoting from a participant of
% Wallace et al's workshop. If the turn-taking aspect of improvisational
% dancing is less, then an effective communication framework could either
% be impossible or not useful, and rather focusing on building a shared
% image is more important. However, one form of turn-taking discussed
% by Wallace is the breaking of shared images. This is the process of
% switching the direction of the creative work and starting in a new
% direction. Participants idenfied this to being an important expectation
% they have from their dance partner. So maybe rather than taking turns,
% the AI need to identify when the user is loosing inspiration and provoke
% them back into a leading state.

... performed a user study to analyze the effectiveness of two-way
communication in human-AI co-creative system. The system they studied
was called: "Creative Penpal", which is a co-creative drawing program,
where the AI can generate refined and inspiring sketches from user's
line sketch. The user study learned that users prefer the two-way
communication system, where the AI would use text instructions to
communicate with the user, and provide them with options during their
creative process to see inspiring sketches, provide feedback etc. The
qualitative insights gathered mentioned how the users felt more engaged
when the AI provided feedback, and felt more like working with a partner
which they enjoyed. Another theme that was important was that users
identified they enjoyed having control over the AI's input.

% Both Wallace et al. and Evola et al. identified the importance of having
% intuition and a "shared image" when trying to perform seemlessly.
% Wallace identified that dancers often predict what their partner will
% do, and Evola showed that expert dancers can use context to gain
% understanding of turn-taking cues, while non-dancers need explicit gaze
% exchange as a way to communicate. 

% ... proposed a way to quickly and effectively label interactions using
% three curves:...
% The main problem that this framework experienced is the resolution of
% the curves produced, as shown in their graph, the alignment of the
% curves only aligned on average per minute to 2 minutes, and any
% timeframe studied less than a minute has significant variance. This,
% although could be used as a reward system for machine learning
% algorithms, might not be good for a high quality analysis. However, we
% can still study the effectiveness of implementing this framework to
% automatically encode interaction data in real-time and design a reward
% algorithm to make the system perform better in the interaction.

% A two-way communication system should be explored in our interaction
% system, although, the communication would be different since embodied
% interactions naturally have a communication aspect.

% Turn-taking in speech is a good topic to study and some important
% aspects of turn-taking could be transferred from speech turn-taking to
% dance turn-taking. 
% Thomaz and Chao conducted an experiment to learn about
% turn-taking in human-robot interaction \cite{Thomaz2011}. The user study is setup by having a human and a
% "robot" play a game of simon says, the robot, being teleoperated by a human. The researchers judged each
% potential turn-ending indicator against the time it took for the human
% to react to the sentence and start their action. All indicators that had
% a "negative" reaction time were deemed impossible. This
% resulted in the concept of Minimum Necessary Information (MNI) as the
% primary indicator in this setting, as humans can start doing an action
% after all the necessary words of the sentence are said and the rest is
% redundant. This however is not in an improvisational setting, as all
% actions and all cues are pre-set, and it is easy to predict the
% following words. 

% Skantze did a analysis for conversational turn-taking, which is a under
% a more improvisational setting \cite{Skantze2021}. The concept of prediction and reaction
% are further explored. Prediction was said to play an important factor in
% human to human speech interactions, which is what makes it so smooth,
% but providing turn-yielding cues are also an important step in the
% turn-taking process. The turn-yielding cues are a way for the leader to
% yield their current turn to the follower, and the effects of using the
% cue is said to be additive, so more turn-yielding cues result in a
% better understanding by the follower. But prediction is also an
% important factor, just like it was discovered in \cite{Thomaz2011}. The
% prediction for the experiment ran by Thomaz and Chao are the MNI point,
% where the human can predict the rest of the words, as the phrases are
% pre-set.

% The concept of breaking shared images from Wallace et al.'s work, can
% fit into the turn-taking paradigm where breaking of shared image is a
% way that the partner has used to take the leadership and shift the
% direction of the dance.

% The theme of AI bringing more to the table is explored in both Wallace
% et al., and Winston and Magerko's work \cite{Wallace2023,
% Winston2017}. The dance professionals from \cite{Wallace2023}
% expressed that they would expect their dance partner to be able to shift
% the tone of the improvisation to generate more inspiration and keep the
% improvisation going. This means bringing something different, like doing
% the opposite of what they are doing. Similarly, \cite{Winston2017},
% although only 2 of the users expressed this, it is still a point made,
% during interactions with TT-VAI, that, they liked it when the AI was
% able to do more than just mimic. And although mimicry
% had a positive reaction by the non-dancers from \cite{Winston2017}, it
% was observed from the experiment in \cite{Wallace2023}, that the
% dance professionals rarely mimicked their partner but sometimes copy
% things like the trajectory of movement or mirroring their use of space.
% This means something that the public could be into, might be less
% inspiring for professional dancers. This could mean that even with a
% user led interaction, the AI can take the role of the leader when the
% user seem disengaged and running out of ideas, then taking the dance in
% a different direction to potentially generate some more interest and inspiration.

% Another new concept for turn-taking that is particular to dance, is the
% perception of leadership state. As in speech, it is obvious who is
% leading and who is following, but in fluid interactions like dancing,
% the leadership state has to be inferred by both parties. This could
% result in a conflict of state, where multiple leaders exist or
% no-leaders exist at once. The work by Winston and Magerko only
% considered the AI agent's perception of who the leader and follower is,
% and did not take into account the user's perception. This should also be
% explored further as a way to improve the user's experience.

% The turn-taking model of expert dancers can potentially be modeled to
% allow a co-creative dance agent to understand turn-taking cues and
% perform seemlessly with dancer professionals. The turn-taking for
% non-dancers, however, is more complicated, as chances for the
% non-dancers to learn the cues and be able to integrate that into their
% mental model is likely impossible. However, as Winston and Magerko
% suggested, casual users are likely more into user led interactions, or
% at least biased towards that. The difference of expert dancers and
% casual users interacting with a turn-taking model like TT-VAI should be
% investigated to gain insights into if turn-taking should be considered
% at all for a dance robot or should it be full or biased towards user led interaction.

\subsection{Dance AI and deep learning}

Machine learning and deep learning has been a popular topic in recent
years. Showing incredible results for text generation, image generation
and much more. Using deep learning techniques to train machine learning
models could enable the generation of realistic responses to user's full
body inputs in a VR or public installation setting.  This can not only
prompt the users to explore different movements in order to have a
better embodied experience, not also prompt user interactions with the
installation, or become a potent tool for co-creative purposes
\cite{Wallace2023}.  Different techniques and models will be reviewed
and examined on their abilities to generate realistic, diverse and
real-time dances for the purpose of an interactive AI agent.

Alemi et al. explored the idea of an interactive AI agent
\cite{Alemi2017}. Alemi et al. compared the Factored Conditional
Restricted Boltzman Machine (FCRBM) and a Long Short Term Memory (LSTM)
network. And at the time, there was not a large public annotated dance
dataset available like AIST++ \cite{Li2021}, so Alemi et al. had to
record their own dance data which only consisted of 4 dance performances
and a total of 23 minutes of dance and audio data.

Bailando++ is neural netowrk model that generates dances based off of
the previously generated dance sequences \cite{Siyao2023}. The
Bailando++ model is a VQVAE and a Generative Pre-trained Transformer
(GPT) that generates dances from a previous dance sequence and dances in sync
to the music. The model is trained to dance to the music through
the "Actor Critic" learning stage which leverages
reinforcement learning and uses beat-alignment as part of the reward function. This
model was able to achieve top-of-the-line results in motion quality, as
well as motion diversity compared to other
popular dance AI models at the time, including DanceNet,
DanceRevolution, FACT and Li et al. Bailando++ also preformed well in
the user study where users are shown 60 pairs of dances by different
models and voted on "which one is dancing better to the music", where it
was able to achieve at least 88\% win rate against all of the models.
Although Bailando++ focused heavily on the ability to dance to the
music, it is likely that for the purpose of our experiments, the ability
to dance to the music is not as important, as care more about the
ability to prompt interaction. But the technique of using actor-critic
learning can be used in our own model.

Dance with you (DanY) \cite{Yao2023} is a neural network model that generates
dances for a partner dancer for a lead dancer. The model uses a three
stage network that also leverages a VQVAE for encoding and decoding, and
U-Net Models. VQVAE is an auto encoder network which can turn complicated dance data sequences into quantized
codes from a finite code book that is learned through the training of
the VQVAE, and the U-Net takes noised data and turns them into dances
features in the code book, which turns random gaussian noise into
realistic dances. The difference of the DanY model is that not only does
it generate from the condition of audio data like many other models, but
it also generates based on the condition of the lead dancer's dance
sequence. This is important for us since we want to deploy an
interactive AI agent which dances in accordance to the lead dancer, who,
in this case, is the user. The quantitative results from this 
Their proposed AIST-M dataset is a dance dataset that contains
Lead-Partner dancer pair annotation great for training models to
generate partner dances from a lead dance sequence. The techniques they used followed that of the creation of the
AIST++ dataset \cite{Li2021} including tracking, SMPL mesh fitting, and
optimization for filtering out undesirable frames to ensure the quality
of the dance data. The proposed AIST-M dataset will be incredibly useful
for our own models' training and analysis.

\section{Discussion}

TODO: write
% introduction

\subsection{Interaction Design}

TODO: write
% analysis of interaction design and final interaction design framework,
% and further work to be done

\subsection{AI Model With Regards to Interaction}

TODO: write
% analysis of existing AI models, and what to adopt, what to try, and
% how to design to facilitate high quality interaction

\subsection{Experiments and Analysis}

TODO: write
% analysis of experiment technique that can be adopted and analysis
% methods for the findings

\section{Summary}

TODO: write
% summary

\bibliographystyle{plain} 
\bibliography{mybib}

\end{document}
\endinput
